Fluent statistical computing interfaces for biological data analysis

### 2020-02-24 Rmd/05-embeddings.Rmd
update toc; rebuild
add abstract

@@

### Case Study 2: well-clustered smallish single cell

### Case Study 3: largish single cell data

### Case Study 4: non-spherical clusters, pdfsense

>>>>

There has been a rapid uptake in the use of non-linear dimensionality reduction (NLDR) methods such as t-distributed stochastic neighbour embedding (t-SNE) in the natural sciences as part of cluster orientation and dimension reduction workflows. The appropriate use of these methods is made difficult by their complex parameterisations and the multitude of decisions required to balance the preservation of
local and global structure in the resulting visualisation. We present a visual analytics framework for the pragmatic usage of NLDR methods by combining them with a technique called the tour. A tour is a sequence of interpolated linear projections of multivariate data onto a lower dimensional space. The sequence is displayed as a dynamic visualisation, allowing a user to see the shadows the high-dimensional data casts in a lower dimensional view. By linking the tour to a view
obtained from an NLDR method, we can preserve global structure and through user interactions like spatial linked brushing observe where
the NLDR view may be misleading. We display show several case 
studies from single cell genomics, that our approach is useful for
cluster orientation tasks. 
The implementation of our framework is available as an R package called `liminal` available at https://github.com/sa-lee/liminal.

@@

### Case Study 2: Clustering PBMC 10x single cell RNA-seq data

### Case Study 3: Single cell mouse retina data
